Investigating factors that may influence COVID-19 survival

### 2022-01-18 paper.Rmd
Update paper.Rmd

---
title: Investigating factors that may influence COVID-19 survival
author:
  - name: 36112985
    email: 36112985@lancaster.ac.uk
    affiliation: Lancaster Medical School
    corresponding: 36112985@lancaster.ac.uk
    affiliation: 
      - Lancaster Medical School
address:
  - code: Lancaster Medical School
    address: Lancaster Medical School, Faculty of Health & Medicine, University of Lancaster
abstract: |
  Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur eget porta erat. Morbi consectetur est vel gravida pretium. Suspendisse ut dui eu ante cursus gravida non sed sem. Nullam sapien tellus, commodo id velit id, eleifend volutpat quam. Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus. Nunc pellentesque pretium diam, quis maximus dolor faucibus id. Nunc convallis sodales ante, ut ullamcorper est egestas vitae. Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.

author_summary: |
  Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur eget porta erat. Morbi consectetur est vel gravida pretium. Suspendisse ut dui eu ante cursus gravida non sed sem. Nullam sapien tellus, commodo id velit id, eleifend volutpat quam. Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus. Nunc pellentesque pretium diam, quis maximus dolor faucibus id. Nunc convallis sodales ante, ut ullamcorper est egestas vitae. Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.

@@

## Null Survival Curve

* Complete Case
* Imputation Case

## Uni-variate Analysis

* The table ... Cox

## Adjusted Analysis via Restricted Mean Survival Time

The proportional hazard assumption does not hold ...

# Results

# Discussion

Within a missing values setting, there are 2 options w.r.t. predictor effect analysis [@steyerberg2010]

* complete case analysis for the uni-variate analysis, and complete case predictors & imputed confounding variables for adjusted analysis.
* uni-variate and adjusted analysis after imputation of all missing values.

The investigation opted for the latter, especially because ...

## Bias

Possible bias points

* By virtue of the study's design pre-study--admission differences between hospitals is possible due to the ambiguity of the study's patient recruitment terms, and this might lead to post-study differences.  In a nutshell, the study is susceptible to selection bias. [Trochim]

* Missing data [@sterne2009]

# Conclusion

The analysis of missing values hints at flaws in data collection.

>>>>

---
title: Investigating factors that may influence COVID-19 survival
author:
  - name: 36112985
    email: 36112985@lancaster.ac.uk
    affiliation: Lancaster Medical School
    corresponding: 36112985@lancaster.ac.uk
address:
  - code: Lancaster Medical School
    address: Lancaster Medical School, Faculty of Health & Medicine, University of Lancaster
abstract: |
  **OBJECTIVE** To investigate, amongst a set of probable prognostic factors, which factors may influence coronavirus 19 disease survival probabilities.  **DESIGN** Prospective cohort study; ongoing.  **SETTING** The International Severe Acute Respiratory and Emerging Infections Consortium (ISARIC) World Health Organization (WHO) Clinical Characterisation Protocol UK (CCP-UK) study, which enrols in-patients at at-least 260 Englsnd, Scotland, and Wales hospitals; the ISARIC Coronavirus Clinical Characterisation Consortium (ISARIC 4C) conducts the study. The investigation's patients are patients enrolled in a participating England hospital between 10 February 2020 and 5 July 2020.  PARTICIPANTS  Each study enrollee has a confirmed SARS-CoV-2 infection, or a high infection likelihood.  The investigation's patients are members of age groups *30 - 39*, *40 - 49*, and higher.  **OUTCOME** Patient survival.  **RESULTS** Inconclusive.  **CONCLUSIONS**  Insufficient spectrum of factors.

@@
